Improving \textsl{Gaia} parallaxes with a data-driven model \\ of the color--magnitude diagram

### 2017-06-02 paper/paper.tex
data figure

We use stars crossmatched in \tgas\ and \tmass\, that also lie within the observing footprint of \panstarrs\ to access the Greene 3D dust model. We require the photometry have real values, and nonzero, real errors, and remove a small selection of \tmass\ stars that have zero color and zero J band magnitude.

>>>>

We use stars crossmatched in \tgas\ and \tmass\, that also lie within the observing footprint of \panstarrs\ to access the Greene 3D dust model. We require the photometry have real values, and nonzero, real errors, and remove a small selection of \tmass\ stars that have zero color and zero J band magnitude. The full data set is visualized in the \cmd\ in Figure \ref{fig:data}. The left panel shows the point estimates of the color and absolute magnitude, using the point estimate of the parallax from \gaia, and the $1\sigma$ and $2\sigma$ contours of the distribution. The right panel shows a subset of the data with it's associated error bars. The uncertainties in the colors are fairly well behaved, but the large uncertainties in the absolute magnitude are due to the large uncertainties in the parallax measurements.
